Using a Two-Layer Neural Network and Physicochemical Properties to Classify Glass for Forensic Analysis

### 2017-06-30 Paper/paper.tex
Experimental Setup

@@

\pagebreak
\appendix

@@

\begin{lstlisting}[style = Python]
if j == 0:
	val_fail = []
elif ce_v[j] > ce_v[j-1]:
	val_fail.append(1)
	if len(val_fail) == 5:
		print 'Validation error has increased for 5 consecutive epochs. Early stopping at epoch {}'.format(j)
		break
else:
	val_fail = []
\end{lstlisting}

>>>>

\subsection{Testing the Network}
Testing the network is a simple process since the network is trained and we just need to feed the inputs in to the network. Since the transfer function in the output layer is the \emph{softmax} function, the network output is the class probabilities between 0 and 1. Once the class probabilities are predicted, we need to use these to convert the probabilities to class predictions. To do this, we use 0.5 as the cutoff, so if one neuron receives a higher probability than the other, that one is chosen to be the positive output from the network and the other is assigned to be null. Then, we compare the predictions to the target which tells us the true class. Using this information, we can calculate classification error, accuracy, true and false positive rates, and construct a confusion matrix. We use all of these as performance metrics in discuss them in the next section. The code used to test the network can be found in Appendix F.

@@

\appendix

@@

\begin{lstlisting}[style = Python]
if j == 0:
	val_fail = []
elif ce_v[j] > ce_v[j-1]:
	val_fail.append(1)
	if len(val_fail) == 5:
		print 'Validation error has increased for 5 consecutive epochs. Early stopping at epoch {}'.format(j)
		break
else:
	val_fail = []
\end{lstlisting} 
\pagebreak

\section{Testing the Network}
The code below shows the code used to test the network and calculate the performance metrics.

\begin{lstlisting}[style = Python]
# --------------------- confusion matrix ---------------------
actual = pd.Series(test.iloc[:, -2], name='Actual')  # actual values (targets)
input = np.matrix(test.iloc[:, slice(0, num_inputs)]).transpose()  # network inputs, p
nlayer1.FP(input)  # layer 1 net-input
nlayer2.FP(nlayer1.a)  # layer 2 net-input
predict = nl.classify(nlayer2.a)  # predicted values from network
predict = np.array(predict).flatten()
predict = pd.Series(predict, name='Predicted')
confusion = pd.crosstab(actual, predict, margins=False)  # create confusion matrix
confusion = confusion.astype(float)  # convert values to floats
print confusion  # output confusion matrix to the console
# --------------------- accuracy metrics ---------------------
ERR = (confusion.loc[0, 1] + confusion.loc[1, 0]) / len(predict)
ACC = 1 - ERR
FPR = confusion.iloc[0, 1] / (confusion.iloc[0, 1] + confusion.iloc[0, 0])
TPR = confusion.iloc[1, 1] / (confusion.iloc[1, 0] + confusion.iloc[1, 1])
\end{lstlisting}
